Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/intro.tex
Typos

Code that handles untrusted inputs, such as processing network
data or parsing a file, is error-prone and is often exploited by
attackers.  This is in part because attackers have precise control
over the inputs to that code, and can craft inputs that trigger
subtle corner cases in input processing.  For example, the libpng image decompression
library has had 24 remotely exploitable vulnerabilities from 2007 to
2013~\cite{cvedetails:libpng},
and Adobe's PDF and Flash viewers have been notoriously
plagued by input processing vulnerabilities.  Even relatively
simple formats, such as those used by the zlib compression
library, have had input processing vulnerabilities in the
past~\cite{cvedetails:zlib}.

@@

Third, many data formats contain redundancies, such as repeating information in multiple structures.
Applications usually do not explicitly check for consistency, and if different applications use
different instances of the same value, an attacker can craft input that causes inconsistencies.
Furthermore, security vulnerabilities can occur when an application assumes two repetitions of the
same data to be consistent, such as allocating a buffer based on the value of one size field and copying into
that buffer based on the value of another.

Finally, real-world data formats, for example PNG or PDF,  are hard to represent with
existing parser generators. Those parsers cannot directly deal with length or checksum fields
directly, so either the programmer has to write potentially unsafe code to deal with such features
or build contrived grammar constructs, such as introducing one grammar rule for each possible value
of a length fields. Offset fields usually require the programmer to manipulate a parser's internal
state to re-position its input. More complicated transformations on the external format, such as
compressed data, cannot be implemented at all.

>>>>

Code that handles untrusted inputs, such as processing network
data or parsing a file, is error-prone and is often exploited by
attackers.  This is in part because attackers have precise control
over the inputs to that code, and can craft inputs that trigger
subtle corner cases in input processing.  For example, the libpng image decompression
library has had 24 remotely exploitable vulnerabilities from 2007 to
2013,\footnote{\url{http://www.cvedetails.com/vulnerability-list/vendor_id-7294/Libpng.html}}
and Adobe's PDF and Flash viewers have been notoriously
plagued by input processing vulnerabilities.  Even relatively
simple formats, such as those used by the zlib compression
library, have had input processing vulnerabilities in the
past.\footnote{\url{http://www.cvedetails.com/vulnerability-list/vendor_id-72/product_id-1820/GNU-Zlib.html}}

@@

Third, many data formats contain redundancies, such as repeating information in multiple structures.
Applications usually do not explicitly check for consistency, and if different applications use
different instances of the same value, an attacker can craft inputs that cause inconsistencies.
Furthermore, security vulnerabilities can occur when an application assumes two repetitions of the
same data to be consistent, such as allocating a buffer based on the value of one size field and copying into
that buffer based on the value of another.

Finally, real-world data formats, for example PNG or PDF,  are hard to represent with
existing parser generators. Those parsers cannot directly deal with length or checksum fields
directly, so either the programmer has to write potentially unsafe code to deal with such features
or build contrived grammar constructs, such as introducing one grammar rule for each possible value
of a length fields. Offset fields usually require the programmer to manipulate a parser's internal
state to re-position its input. More complicated transformations on the external format, such as
compressed data, cannot be represented at all.

### 2014-05-01 paper/osdi14/relwk.tex
Typos

Parser generators for binary protocols were first introduced by the
Hammer~\cite{hammer-parser} parser.
While previous parser generators could also be used to write grammars
for binary protocols,\footnote{Theoretically speaking, the alphabet
over which a grammar is an  abstract set, so most algorithms work
just as well on an alphabet of $\{0,1\}$.} doing so is practically
inconvenient. Hammer allows the programmer to specify a grammar in
terms of bits and bytes instead of characters. Common concerns, such as
endianness and bit-packing are transparently hidden by the library.

@@

Nail improves upon Hammer in three ways. First, Nail  generates output besides recognizing input.
Second, Nail does not require the programmer to write potentially insecure semantic actions. Last,
Nail's structural dependencies and transformations allow it to work with protocols Hammer cannot recognize, such as
protocols with offset fields or length fields (Hammer has extremely limited support for length
fields: it can parse arrays immediately preceded by their length).

@@

The second class is logic errors, where application code misinterprets input data. Safe languages
and exploit mitigation technologies do not help against such vulnerabilities. This can lead to
serious security consequences when two systems disagree on the meaning of a network packet or a
signed message, as in iOS\footnote{The XNU kernel and the user code-signing verifier interpret
  executable metadata differently, so the code signature sees different bytes at a virtual address
  than the executable that runs.}~\cite{evaders6} and Android~\cite{saurik-masterkey}code signing
and even the X.509 protocol underlying SSL~\cite{DBLP:conf/fc/KaminskyPS10}. Logic errors are often
causing memory corruption bugs as well, for example when a protocol stores the size of a buffer in
two places and the implementation does not check their consistency. These mistakes are
highly application-specific, and are difficult to mitigate using existing techniques, and these
mistakes can occur even in high-level languages that guarantee memory safety. By allowing developers
to specify their data format just once, Nail avoids logic errors and inconsistencies in parsing and
output generation.

@@

Proper input recognition has been shown to be an excellent way of eliminating ambiguous inputs. In
one case, a PDF parser implemented in Coq could eliminate over $95\%$ of known malicious
PDFs~\cite{Bogk-PDF}. The same project also produced a ``counter-example'' PDF that triggered
numerous bugs in other PDF parsers. However, manually writing parser code and proving unambiguity
does not scale to the number of file formats and protocols in existence and might result in parser
code tied to one specific application.

>>>>

Parser generators for binary protocols were first introduced by the
Hammer~\cite{hammer-parser} parser.
While previous parser generators could also be used to write grammars
for binary protocols,\footnote{Theoretically speaking, the alphabet
over which a grammar is an  abstract set, so most algorithms work
just as well on an alphabet of $\{0,1\}$.} doing so is practically
inconvenient. Hammer allows the programmer to specify a grammar in
terms of bits and bytes instead of characters. Common concerns, such as
endianness and bit-packing are handled transparently.

@@

Nail improves upon Hammer in three ways. First, Nail  generates output besides recognizing input.
Second, Nail does not require the programmer to write potentially insecure semantic actions. Last,
Nail's structural dependencies and transformations allow it to work with protocols Hammer cannot recognize, such as
protocols with offset fields or length fields, although Hammer has special facilities for  arrays immediately preceded by their length.

@@

The second class is logic errors, where application code misinterprets input data. Safe languages
and exploit mitigation technologies do not help against such vulnerabilities. This can lead to
serious security consequences when two systems disagree on the meaning of a network packet or a
signed message, as in iOS\footnote{The XNU kernel and the user-mode code-signing verifier interpret
  executable metadata differently, so the code signature sees different bytes at a virtual address
  than the executable that runs.}~\cite{evaders6} and Android~\cite{saurik-masterkey}code signing
and even the X.509 protocol underlying SSL~\cite{DBLP:conf/fc/KaminskyPS10}. Logic errors are often
causing memory corruption bugs as well, for example when a protocol stores the size of a buffer in
two places and the implementation does not check their consistency. These mistakes are
highly application-specific, and are difficult to mitigate using existing techniques, and these
mistakes can occur even in high-level languages that guarantee memory safety. By allowing developers
to specify their data format just once, Nail avoids logic errors and inconsistencies in parsing and
output generation.

@@

Proper input recognition has been shown to be an excellent way of eliminating ambiguous inputs. In
one case, a PDF parser implemented in Coq rejects over $95\%$ of known malicious
PDFs~\cite{Bogk-PDF}. The same project also produced a ``counter-example'' PDF that triggered
numerous bugs in other PDF parsers. However, manually writing parser code and proving unambiguity
does not scale to the number of file formats and protocols in existence and might result in parser
code tied to one specific application.
